### 2023-10-25 generalExploration.Rmd
replace index by name of dead invidual seems to fix some problem related to #1

reproduction <- function(p1,p2,tp,i=NULL){

    stopifnot(p1$community==p2$community)
    traits=ifelse(sample(c(0,1),length(tp$s),replace=T),p1$traits,p2$traits)
    if(!is.null(i))id=as.numeric(i)+1
    print(id)
    list(
         id=as.character(id),
         traits=traits,
         age=0,
         community=p1$community,
         sex=sample(c("F","M"),1),
         repro=FALSE,
         partner=-1
    )
}

@@

tstep=1000
popsize=c()
popsum=list()
for(time in 1:tstep){
    for(i in sample(1:length(population))){
        ind=tryCatch(population[[i]]$id,error=function(e)NULL)
        if(!is.null(ind)){
            ##ageing
            population[[ind]]$age=population[[ind]]$age+1

@@

            #Handle deaths
            if(runif(1)<d){
                if(partner>0) population[[partner]]$partner=-1
                population[i]=NULL
                print(paste("dead ind",i))
            }
        }

>>>>

reproduction <- function(p1,p2,tp,i=NULL){
    stopifnot(p1$community==p2$community)
    traits=ifelse(sample(c(0,1),length(tp$s),replace=T),p1$traits,p2$traits)
    if(!is.null(i))id=as.numeric(i)+1
    print(id)
    list(
         id=as.character(id),
         traits=traits,
         age=0,
         community=p1$community,
         sex=sample(c("F","M"),1),
         repro=FALSE,
         partner=-1
    )
}

@@

tstep=1000
popsize=c()
popsum=list()
for(time in 1:tstep){
    print(paste("------",time,"------"))
    for(i in sample(1:length(population))){
        ind=tryCatch(population[[i]]$id,error=function(e)NULL)
        if(!is.null(ind)){
            ##ageing

            population[[ind]]$age=population[[ind]]$age+1

@@

            #Handle deaths
            if(runif(1)<d){
                if(partner>0) population[[partner]]$partner=-1
                population[[ind]]=NULL
                print(paste("dead ind",ind))
            }
        }
